The Increased Effect of Elections and Changing Prime Ministers on Topics Discussed in the Australian Federal Parliament between 1901 and 2018

### 2019-11-25 outputs/docs/paper/paper-hansarddataonly_test.Rmd
Update paper

---
output:
  bookdown::pdf_document2:
    citation_package: natbib
    keep_tex: false
    fig_caption: true
    number_sections: true
    latex_engine: pdflatex
    template: svm-latex-ms.tex
title: "The Increased Effect of Elections and Prime Ministers on Discussion in the Australian Federal Parliament between 1901 and 2018"
thanks: "Thank you to Chris Cochrane, Dan Simpson, Jill Sheppard, John McAndrews, John Tang, Leslie Root, Martine Mariotti, Matt Jacob, Matthew Kerby, Myles Clark, Ruth Howlett, Tianyi Wang, Tim Hatton, and Zach Ward for their helpful suggestions; and to the UC Berkeley Demography Department for the use of their computing resources. We are grateful for the many excellent comments that we received from seminar participants at the ANU SPIR, the ANU RSE, the Australian Parliamentary Library, the Max Planck Institute for Demographic Research, the U of T Political Behavior Group, and the 2019 PSA Political Methodology Conference. The code and data for this paper is available at: https://github.com/RohanAlexander/hansard. Comments and suggestions on the `r format(Sys.time(), '%d %B %Y')` version of this paper welcome at: rohan.alexander@anu.edu.au."
author:
- name: Rohan Alexander
  affiliation: Australian National University
- name: Monica Alexander
  affiliation: University of Toronto
abstract: "A large part of politics consists of reacting to events, but not all events provoke a reaction. As such, understanding political behaviour requires examining the reaction to events and how this changes over time. We systematically analyse how discussion in the Australian Federal Parliament changes in response to two types of events: elections and changed prime ministers. To do this we first create a new dataset of what was said in the Australian Federal Parliament from 1901 through to 2018 based on available public records. We reduce the dimensionality of this dataset using a correlated topic model, relate those topics to the Comparative Agendas Project, and then analyse the effect of these two types of events using a Bayesian hierarchical Dirichlet model that has several advantages over existing models. We find that: changes in prime minister tend to be associated with topic changes even when the party in power does not change; and elections that do not result in a change in prime minister are rarely associated with topic changes in the first half of our sample, but have been increasingly significant since the 1980s."
keywords: "text-as-data, Australian politics, unsupervised machine learning, Bayesian hierarchical Dirichlet model, Comparative Agendas Project"
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: mathpazo
fontsize: 12pt
toc: FALSE
# spacing: double
bibliography: ../bibliography.bib
biblio-style: apsr
endnote: no

@@

Of the 36 prime ministers over this period, we find that 17 of them were significantly different to the prime minister that preceded them, after we account for and remove some that had especially short terms. The three earliest of them occur in the first decade after Federation, and to a certain extent this may be due to the variety of the issues that had to be addressed in those initial years. Joseph Cook's time as prime minister is found to be significantly different to that of his predecessor, Andrew Fisher, although it may be that this is due to World War I.

The second Menzies term, beginning in 1949, is the next government that is significantly different to its predecessor. The other governments that are different are concentrated in the second half of our sample, with three of them being in the past twenty years. Similarly, of the 45 general elections that have been held we find that 14 of them define periods that were significantly different to their immediate predecessor. 1974, 1980, 1990, 1998, 2004, and 2007 stand out as elections where the government did not change, but the model suggests there was considerable change in the topics discussed in parliament.

The second Menzies term was associated with a variety of changes compared with the preceding Chifley Government. Chifley had governed through the end of World War II and the difficult economic times that followed. There was also a large increase in the number of seats in the House of Representatives at the 1949 election. Many new politicians entered parliament, and this changed representation may also have been partly to do with the changed distribution of discussion topics, although further investigation of this is left for future work. The sixteen-year length of the second Menzies term, and better economic conditions over this time make it understandable why parliamentary discussion would have been different. There were six elections within the second Menzies term. Three toward the middle of that government were associated with significant changes in the topics discussed.

Menzies was succeeded  Holt in January 1966. This is an example where there was a change in prime minister without an election, as the next election only happened in November 1966. We find that Holt is different to Menzies.

<!-- In Figures \@ref(fig:muelectionall) we compare the topics during Menzies' final term with the topics of Holt. -->

<!-- ```{r muelectionall, cache = TRUE, echo = FALSE, fig.cap = "Differences between various elections", out.width = '100%'} -->
<!-- knitr::include_graphics("../../figures/mu_election-differences.pdf") -->
<!-- ``` -->

Whitlam's term is especially interesting as we find a difference in the topics after he was first elected in December 1972, compared with his second election win in May 1974. Figure \@ref(fig:muelectionall) compares the topics that are significant before and after the election.

Howard is also interesting because of the significant differences between elections. For instance, each of the election periods is associated with fairly substantial differences compared with the preceding election periods, and all are actually significantly different at the 95 per cent level. Figure \@ref(fig:muelectionall) compares the topics that are significant in the different elections that Howard won.

To a certain extent the change after the November 2001 election is expected because of the 9/11 terrorist attacks that had only occurred two months earlier, the Bali Bombings that occurred in October 2002, and the dramatic increase in the discussion related to terrorism and conflict over these years. However, the change in 1998 and 2004 is more unexpected. Although Howard is the second-longest serving prime minister and commonly thought of as a period of stability because the senior ministers were consistent as well, it might be that it is better to think of Howard as a combination of three or four different periods and that Howard reinvented itself over this period.

>>>>

---
output:
  bookdown::pdf_document2:
    citation_package: natbib
    keep_tex: false
    fig_caption: true
    number_sections: true
    latex_engine: pdflatex
    template: svm-latex-ms.tex
title: "A Text Corpus based on the Hansard of the Australian Federal Parliament between 1901 and 2018"
thanks: "Thank you to Monica Alexander for her helpful suggestions; and to the UC Berkeley Demography Department for the use of their computing resources. The code and data for this paper is available at: https://github.com/RohanAlexander/hansard. Comments and suggestions on the `r format(Sys.time(), '%d %B %Y')` version of this paper welcome at: rohan.alexander@anu.edu.au."
author:
- name: Rohan Alexander
  affiliation: University of Toronto
abstract: "A large part of politics consists of reacting to events, but not all events provoke a reaction. As such, understanding political behaviour requires examining the reaction to events and how this changes over time. We systematically analyse how discussion in the Australian Federal Parliament changes in response to two types of events: elections and changed prime ministers. To do this we first create a new dataset of what was said in the Australian Federal Parliament from 1901 through to 2018 based on available public records. We reduce the dimensionality of this dataset using a correlated topic model, relate those topics to the Comparative Agendas Project, and then analyse the effect of these two types of events using a Bayesian hierarchical Dirichlet model that has several advantages over existing models. We find that: changes in prime minister tend to be associated with topic changes even when the party in power does not change; and elections that do not result in a change in prime minister are rarely associated with topic changes in the first half of our sample, but have been increasingly significant since the 1980s."
keywords: "text-as-data, Australian politics, unsupervised machine learning, Bayesian hierarchical Dirichlet model, Comparative Agendas Project"
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: mathpazo
fontsize: 12pt
toc: FALSE
# spacing: double
bibliography: ../bibliography.bib
biblio-style: apsr
endnote: no

@@

Of the 36 prime ministers over this period, we find that 17 of them were significantly different to the prime minister that preceeded them, after we account for and remove some that had especially short terms. The first three that are significant occur in the first decade after Federation. To a certain extent, this may be due to the variety of the issues that had to be addressed in those initial years. The fourth prime minister that was significantly different to his predecessor was Joseph Cook. This coincided with the initial period of World War I and it may be that this is the reason for difference, compared with his predecessor, and successor Andrew Fisher.

Stanley Bruce is significantly different from his predecessor Billy Hughes, even though they were ostensibly from the same party. Hughes had been prime minister for over six years, and Bruce was a compromise choice in order to form a coalition.

<!-- The Lyons 14 -->

<!-- The second Menzies term, beginning in 1949, is the next government that is significantly different to its predecessor. The other governments that are different are concentrated in the second half of our sample, with three of them being in the past twenty years. Similarly, of the 45 general elections that have been held we find that 14 of them define periods that were significantly different to their immediate predecessor. 1974, 1980, 1990, 1998, 2004, and 2007 stand out as elections where the government did not change, but the model suggests there was considerable change in the topics discussed in parliament. -->

<!-- The second Menzies term was associated with a variety of changes compared with the preceding Chifley Government. Chifley had governed through the end of World War II and the difficult economic times that followed. There was also a large increase in the number of seats in the House of Representatives at the 1949 election. Many new politicians entered parliament, and this changed representation may also have been partly to do with the changed distribution of discussion topics, although further investigation of this is left for future work. The sixteen-year length of the second Menzies term, and better economic conditions over this time make it understandable why parliamentary discussion would have been different. There were six elections within the second Menzies term. Three toward the middle of that government were associated with significant changes in the topics discussed.  -->

<!-- Menzies was succeeded  Holt in January 1966. This is an example where there was a change in prime minister without an election, as the next election only happened in November 1966. We find that Holt is different to Menzies.  -->

<!-- <!-- In Figures \@ref(fig:muelectionall) we compare the topics during Menzies' final term with the topics of Holt. -->

<!-- <!-- ```{r muelectionall, cache = TRUE, echo = FALSE, fig.cap = "Differences between various elections", out.width = '100%'} --> 
<!-- <!-- knitr::include_graphics("../../figures/mu_election-differences.pdf") --> 
<!-- <!-- ``` -->

<!-- Whitlam's term is especially interesting as we find a difference in the topics after he was first elected in December 1972, compared with his second election win in May 1974. Figure \@ref(fig:muelectionall) compares the topics that are significant before and after the election. -->

<!-- Howard is also interesting because of the significant differences between elections. For instance, each of the election periods is associated with fairly substantial differences compared with the preceding election periods, and all are actually significantly different at the 95 per cent level. Figure \@ref(fig:muelectionall) compares the topics that are significant in the different elections that Howard won. -->

<!-- To a certain extent the change after the November 2001 election is expected because of the 9/11 terrorist attacks that had only occurred two months earlier, the Bali Bombings that occurred in October 2002, and the dramatic increase in the discussion related to terrorism and conflict over these years. However, the change in 1998 and 2004 is more unexpected. Although Howard is the second-longest serving prime minister and commonly thought of as a period of stability because the senior ministers were consistent as well, it might be that it is better to think of Howard as a combination of three or four different periods and that Howard reinvented itself over this period. -->

### 2019-11-25 outputs/docs/paper/paper.Rmd
Update paper

header-includes:
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage[table]{xcolor}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
- \usepackage{subfig}

>>>>

header-includes:
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
# - \usepackage[table]{xcolor}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
- \usepackage{subfig}

### 2019-11-25 outputs/docs/paper/paper_MA_structure_edit.Rmd
Update paper

---
output:
  bookdown::pdf_document2:
    citation_package: natbib
    keep_tex: false
    fig_caption: true
    number_sections: true
    latex_engine: pdflatex
    template: svm-latex-ms.tex
title: "The Increased Effect of Elections and Changing Prime Ministers on Topics Discussed in the Australian Federal Parliament between 1901 and 2018"
thanks: "Thank you to Chris Cochrane, Dan Simpson, Jill Sheppard, John McAndrews, John Tang, Leslie Root, Martine Mariotti, Matt Jacob, Matthew Kerby, Myles Clark, Ruth Howlett, Tianyi Wang, Tim Hatton, and Zach Ward for their helpful suggestions; and to the UC Berkeley Demography Department for the use of their computing resources. We are grateful for the many excellent comments that we received from seminar participants at the ANU SPIR, the ANU RSE, the Australian Parliamentary Library, the Max Planck Institute for Demographic Research, the U of T Political Behavior Group, and the 2019 PSA Political Methodology Conference. The code and data for this paper is available at: https://github.com/RohanAlexander/hansard. Comments and suggestions on the `r format(Sys.time(), '%d %B %Y')` version of this paper welcome at: rohan.alexander@anu.edu.au."
author:
- name: Rohan Alexander
  affiliation: Australian National University
- name: Monica Alexander
  affiliation: University of Toronto
abstract: "Politics and discussion in parliament is likely to be influenced by the party in power and associated election cycles. However, little is known about the extent to which these events affect discussion and how this has changed over time. We systematically analyse how discussion in the Australian Federal Parliament changes in response to two types of political events: elections and changed prime ministers. We use a newly constructed dataset of what was said in the Australian Federal Parliament from 1901 through to 2018 based on extracting and cleaning available public records. We reduce the dimensionality of discussion in this dataset by using a correlated topic model to obtain a set of comparable topics over time. We then relate those topics to the Comparative Agendas Project, and then analyse the effect of these two types of events using a Bayesian hierarchical Dirichlet model. We find that: changes in prime minister tend to be associated with topic changes even when the party in power does not change; and the effect of elections has been increasing since the 1980s, regardless of whether the election results in a change of prime minister."
keywords: "text-as-data, Australian politics, unsupervised machine learning, Bayesian hierarchical Dirichlet model, Comparative Agendas Project"
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: mathpazo
fontsize: 12pt
toc: FALSE
# spacing: double
bibliography: ../bibliography.bib
biblio-style: apsr
endnote: no

header-includes:
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage[table]{xcolor}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
- \usepackage{subfig}

@@

What is discussed in parliament is a key indicator of a government's priorities and likely policy outcomes. While in an ideal world, we may hope that topics of discussion represent the most important social, economic and environmental issues for the country at that particular time, in reality, discussion is heavily influenced by party politics, the priorities of the head of government at the time, and where they are in the current election cycle.

For example, XX NEED A BIT OF A LITERATURE REVIEW HERE on papers that look at discussion and political changes?? XX

@@

In this paper, we exame the effect of elections and changes in prime ministers on the topics that are discussed in the Australian Federal Parliament. We construct a new dataset from the text record, known as 'Hansard', of what was said in the Australian Federal Parliament since its inception in 1908, to 2018. The dataset covers records for 7,934 days in the House of Representatives (lower house) and 6,746 days in the Senate (upper house).

@@

The remainder of the paper is structured as follows XX.

@@

The Australian Federal Parliament makes daily Hansard records available online as PDFs and these are considered the official release.[^XMLfootnote] We provide an example of a Hansard PDF page in Appendix \@ref(examplehansardpage). There are XX PDF files that cover the Hansard over the entire period 1901-2018. Our goal is to take these PDFs and convert them into a digitized dataset of text that is able to be analysed.

@@

The creation of the Hansard dataset involves the following steps. Firstly, optical character recognition (OCR) is used to convert static PDFs into digitised text. This creates a text file for each PDF with a single character string. Secondly, as many of the original PDFs contained two columns per page, the text file is reshuffled to ensure the text is in the right order. Thirdly, the text is split out such that it is separated by speaker. This involves XX. Lastly, the dataset is created in tidy format (XX REF here), such that there are columns for speaker, the date, and the text of what was said, and every row refers to a different speaker. XX could add more detail to this paragraph XX

@@

There are 14,680 days of publicly available Hansard records across the two chambers of the Australian Federal Parliament for which we have PDFs. Further summary statistics for this are provided in Appendix \@ref(hansardsummarystatistics). In general, the frequency of sitting days based on information from the Hansard dataset compared to the actual number of sitting days is comparable, almost complete coverage of our dataset. XX MAYBE PULL OUT MORE SUMMARY STATS IN PARTICULAR HIGHLIGHT THE TWO CHAMBERS XX

@@

There are various methods to help determine the appropriate number of topics to specify. Appendix \@ref(selecttopicnumber) contains a discussion of how the number of topics was chosen based on the output of the CTM. However, we found that the optimal number of topics selected was too large to be tractable by our analysis model, and too large to be easily visualised or examined. In addition, many of the topics in the optimal set referred to similar themes, such as budgeting or administrative topics.

For this reason we manually group the topics identified by the CTM into those of the Comparative Agendas Project. XX NEED TO EXPLAIN WHAT THIS IS - I HAVE NO IDEA XX

@@

```{r topwords, echo = FALSE, results = 'asis'}
# 
# top_words %>% 
#   kable("latex", 
#         booktabs = T, 
#         longtable = TRUE, 
#         caption = "The ten words most strongly associated with each topic"
#         ) %>%
#   kable_styling(font_size = 8, 
#                 latex_options = c("repeat_header")
#                 )
```

@@

Figure \@ref(fig:threeexamples) shows the topic model output in the context of three notable periods of Australian political history. 
The first panel of Figure \@ref(fig:threeexamples) is the second Menzies term. The dashed lines show the elections. While the results here abstract from differences based on topic mix, the shape of the distribution seems to be reasonably similar. Given 80 topics, it may be difficult to see differences in the topic mix manually, and so we would like for the analysis model to be able to suggest whether the mix is changing. The second panel shows the 1983 election, and the subsequent change from Fraser to Hawke on 11 March 1983, identified by a dotted line on that date. The distribution of topics seems less bunched after the change, but it is difficult to tell how different it is. We would like the analysis model to be able to distinguish between the two if they seem different. The third panel shows the first Rudd term. The important aspect to note is that the period after the 2007 election and the Rudd term contain essentially the same Hansard dates. The analysis model needs to be able to deal with this situation. XX I FIND THESE FIGURES HARD TO READ... CONSIDER REDOING OR REMOVING XX

@@

There are several outputs of interest from this modelling stage. For example, the model provides estimates of topic prevalence by each sitting period. Figure \@ref(fig:wartopicsgraph) illustrates the estimated topic prevlance by sitting period for topic XX, one of the defense-related topics, overlayed with the daily topic prevalnce (as also illustrated in Figure XX above). This nicely illustrates how the topics change over time, as the daily estimates tend to be quite variable.

@@

We summarise our results in terms of prime ministers in Table \@ref(tab:primeministersresults) and in terms of elections in Table \@ref(tab:electionsresults). These tables focus on prime ministers and elections that were different to the ones that preceded them.[^listfootnote] A total of XX out of the XX prime ministers had significantly different topic discussions than their predecessor. In terms of elections, XX out of a total of XX elections were significant different to the previous cycle.

@@

In Figures \@ref(fig:mugov) and \@ref(fig:muelection) we focus on certain topics to illustrate significant differences between prime ministers and elections, respectively. In the graphs, the points show the estimated value of $\alpha_g$ and $\beta_e$, respectively, for each of the topics specified. The error bars represent 95 per cent Bayesian credible intervals. We have focused on Topics XX here which have to do with war and conflict. Large differences can be seen for XX ADD A BIT OF COMMENTARY HERE XX

@@

Table \@ref(tab:keyeventsresultstable) summarises the days where parliamentary discussion was significantly different from the rest prevailing in that week. XX ADD A BIT OF COMMENTARY HERE XX

@@

<!-- In Figures \@ref(fig:muelectionall) we compare the topics during Menzies' final term with the topics of Holt. -->

<!-- ```{r muelectionall, cache = TRUE, echo = FALSE, fig.cap = "Differences between various elections", out.width = '100%'} -->
<!-- knitr::include_graphics("../../figures/mu_election-differences.pdf") -->
<!-- ``` -->

>>>>

---
output:
  bookdown::pdf_document2:
    citation_package: natbib
    keep_tex: false
    fig_caption: true
    number_sections: true
    latex_engine: pdflatex
    template: svm-latex-ms.tex
title: "The Increased Effect of Elections and Changing Prime Ministers on Topics Discussed in the Australian Federal Parliament between 1901 and 2018"
thanks: "Thank you to Chris Cochrane, Dan Simpson, Edward Morgan, Jill Sheppard, John McAndrews, John Tang, Leslie Root, Martine Mariotti, Matt Jacob, Matthew Kerby, Myles Clark, Ruth Howlett, Tianyi Wang, Tim Hatton, and Zach Ward for their helpful suggestions; and to the UC Berkeley Demography Department for the use of their computing resources. We are grateful for the many excellent comments that we received from seminar participants at the Australian National University (ANU) SPIR, the ANU RSE, the Australian Parliamentary Library, the Max Planck Institute for Demographic Research, the University of Toronto Political Behavior Group, and the 2019 PSA Political Methodology Conference. The code and data for this paper is available at: https://github.com/RohanAlexander/hansard. Comments and suggestions on the `r format(Sys.time(), '%d %B %Y')` version of this paper welcome at: rohan.alexander@utoronto.ca."
author:
- name: Rohan Alexander
  affiliation: University of Toronto
- name: Monica Alexander
  affiliation: University of Toronto
abstract: "Politics and discussion in parliament is likely to be influenced by the party in power and associated election cycles. However, little is known about the extent to which these events affect discussion and how this has changed over time. We systematically analyse how discussion in the Australian Federal Parliament changes in response to two types of political events: elections and changed prime ministers. We use a newly constructed dataset of what was said in the Australian Federal Parliament from 1901 through to 2018 based on extracting and cleaning available public records. We reduce the dimensionality of discussion in this dataset by using a correlated topic model to obtain a set of comparable topics over time. We then relate those topics to the Comparative Agendas Project, and then analyse the effect of these two types of events using a Bayesian hierarchical Dirichlet model. We find that: changes in prime minister tend to be associated with topic changes even when the party in power does not change; and the effect of elections has been increasing since the 1980s, regardless of whether the election results in a change of prime minister."
keywords: "text-as-data, Australian politics, unsupervised machine learning, Bayesian hierarchical Dirichlet model, Comparative Agendas Project"
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: mathpazo
fontsize: 12pt
toc: FALSE
# spacing: double
bibliography: ../bibliography.bib
biblio-style: apsr
endnote: no

header-includes:
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
- \usepackage{subfig}

@@

What is discussed in parliament is a key indicator of a government's priorities and likely policy outcomes. While in an ideal world, we may hope that topics of discussion represent the most important social, economic, and environmental issues for the country at that particular time, in reality, discussion is heavily influenced by party politics, the priorities of the government of the day, and the current election cycle.

<!-- TODO: For example, XX NEED A BIT OF A LITERATURE REVIEW HERE on papers that look at discussion and political changes?? XX -->

@@

In this paper, we examine the effect of elections and changes in prime ministers on the topics that are discussed in the Australian Federal Parliament. We construct a new dataset from the text record, known as 'Hansard', of what was said in the Australian Federal Parliament since its inception in 1908, to 2018. The dataset covers records for 7,934 days in the House of Representatives (lower house) and 6,746 days in the Senate (upper house).

@@

The remainder of the paper is structured as follows. Section \@ref(hansarddata) examines the data that we use; Section \@ref(model) introduces our models; Section \@ref(results) goes into our results; and finally, Section \@ref(discussion) discusses our results and some of the shortcomings.

@@

The Australian Federal Parliament makes daily Hansard records available online as PDFs and these are considered the official release.[^XMLfootnote] We provide an example of a Hansard PDF page in Appendix \@ref(examplehansardpage). There are 14,680 PDF files that cover the Hansard over the entire period 1901-2018. Our goal is to take these PDFs and convert them into a digitized dataset of text that is able to be analysed.

@@

The creation of the Hansard dataset involves the following steps. Firstly, optical character recognition (OCR) is used to convert static PDFs into digitised text. This creates a text file for each PDF with a single character string. Secondly, as many of the original PDFs contained two columns per page, the text file is reshuffled to ensure the text is in the right order. Thirdly, the text is split out such that it is separated by speaker. This involves identifying names and the structure of how speakers are introduced and then splitting based on this. Lastly, the dataset is created in tidy format [@wickham2014tidy], such that there are columns for speaker, the date, and the text of what was said, and every row refers to a different speaker. 
<!-- XX could add more detail to this paragraph XX -->

@@

There are 14,680 days of publicly available Hansard records across the two chambers of the Australian Federal Parliament for which we have PDFs. Further summary statistics for this are provided in Appendix \@ref(hansardsummarystatistics). In general, the frequency of sitting days based on information from the Hansard dataset compared to the actual number of sitting days is comparable, almost complete coverage of our dataset. 
<!-- XX MAYBE PULL OUT MORE SUMMARY STATS IN PARTICULAR HIGHLIGHT THE TWO CHAMBERS XX -->

@@

There are various methods to help determine the appropriate number of topics to specify. Appendix \@ref(selecttopicnumber) contains a discussion of how the number of topics was chosen based on the output of the CTM. However, we found that the optimal number of topics selected was too large to be tractable by our analysis model, and too large to be easily visualised, or examined. In addition, many of the topics in the optimal set referred to similar themes, such as budgeting or administrative topics.

For this reason we manually group the topics identified by the CTM into those of the Comparative Agendas Project. The Comparative Agendas Project provides a classification of a large number of specific issues into a small number of major topics.

@@

<!-- # ```{r topwords, echo = FALSE, results = 'asis'} -->
<!-- # #  -->
<!-- # # top_words %>%  -->
<!-- # #   kable("latex",  -->
<!-- # #         booktabs = T,  -->
<!-- # #         longtable = TRUE,  -->
<!-- # #         caption = "The ten words most strongly associated with each topic" -->
<!-- # #         ) %>% -->
<!-- # #   kable_styling(font_size = 8,  -->
<!-- # #                 latex_options = c("repeat_header") -->
<!-- # #                 ) -->
<!-- # ``` -->

@@

Figure \@ref(fig:threeexamples) shows the topic model output in the context of three notable periods of Australian political history. 
The first panel of Figure \@ref(fig:threeexamples) is the second Menzies term. The dashed lines show the elections. While the results here abstract from differences based on topic mix, the shape of the distribution seems to be reasonably similar. Given 80 topics, it may be difficult to see differences in the topic mix manually, and so we would like for the analysis model to be able to suggest whether the mix is changing. The second panel shows the 1983 election, and the subsequent change from Fraser to Hawke on 11 March 1983, identified by a dotted line on that date. The distribution of topics seems less bunched after the change, but it is difficult to tell how different it is. We would like the analysis model to be able to distinguish between the two if they seem different. The third panel shows the first Rudd term. The important aspect to note is that the period after the 2007 election and the Rudd term contain essentially the same Hansard dates. The analysis model needs to be able to deal with this situation. 
<!-- XX I FIND THESE FIGURES HARD TO READ... CONSIDER REDOING OR REMOVING XX -->

@@

There are several outputs of interest from this modelling stage. For example, the model provides estimates of topic prevalence by each sitting period. Figure \@ref(fig:wartopicsgraph) illustrates the estimated topic prevlance by sitting period for topic 15, one of the defense-related topics, overlayed with the daily topic prevalence (as also illustrated in Figure \@ref(fig:threeexamples) above). This nicely illustrates how the topics change over time, as the daily estimates tend to be quite variable.

@@

We summarise our results in terms of prime ministers in Table \@ref(tab:primeministersresults) and in terms of elections in Table \@ref(tab:electionsresults). These tables focus on prime ministers and elections that were different to the ones that preceded them.[^listfootnote] A total of 17 out of the 36 prime ministerial periods had significantly different topic discussions than their predecessor. In terms of elections, 12 out of a total of 45 elections were significantly different to the previous cycle.

@@

In Figures \@ref(fig:mugov) and \@ref(fig:muelection) we focus on certain topics to illustrate significant differences between prime ministers and elections, respectively. In the graphs, the points show the estimated value of $\alpha_g$ and $\beta_e$, respectively, for each of the topics specified. The error bars represent 95 per cent Bayesian credible intervals. We have focused on Topics 1, 2, 7, 13, 15, 16, 17, and 19 here which have to do with war and conflict. Large differences can be seen at various times.
<!-- XX ADD A BIT OF COMMENTARY HERE XX -->

@@

Table \@ref(tab:keyeventsresultstable) summarises the days where parliamentary discussion was significantly different from the rest prevailing in that week. Notably, considerably more than a majority of these dates occur in the first half of our sample. And a full seven occur in 1909.

@@

In Figures \@ref(fig:muelectionall) we compare the topics during Menzies' final term with the topics of Holt.

```{r muelectionall, cache = TRUE, echo = FALSE, fig.cap = "Differences between various elections", out.width = '100%'}
knitr::include_graphics("../../figures/mu_election-differences.pdf")
```
